Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
intro done

\section{Executive Summary}
\label{sec:summary}
Governor Bryant,\\

@@

While these two strategies can aid you in making decisions for an imminent hurricane, we also have a recommendation for a long-term improvement to all evacuation routes. In our analysis of evacuation throughput, we discovered that the area around George County poses a significant bottleneck for highway traffic. As our analysis will show later in this manuscript, adding an additional highway route from George County to Perry county will significantly shift this bottleneck upward. This would allow more evacuees to escape the most dangerous coastal areas before they are slowed down by a bottleneck. Especially with potentially heavy traffic coming up highway 59 from New Orleans, traffic congestion in the coastal region is a problem requiring a more long term solution.

\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design hurricane evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold ordering an evacuation for as long as is safely possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that the forecasts at the time of the evacuation decision are as accurate as possible. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.

>>>>

\section{Executive Summary}
\label{sec:summary}
\\
Governor Bryant,\\

@@

While these two strategies can aid you in making decisions for an imminent hurricane, we also have a recommendation for a long-term improvement to all evacuation routes. In our analysis of evacuation throughput, we discovered that the area around George County poses a significant bottleneck for highway traffic. As our analysis will show later in this manuscript, adding an additional highway route from George County to Perry county will significantly shift this bottleneck upward. This would allow more evacuees to escape the most dangerous coastal areas before they are slowed down by a bottleneck. Especially with potentially heavy traffic coming up highway 59 from New Orleans, traffic congestion in the coastal region is a problem requiring a more long term solution.\\
\\
\\
Sincerely,\\
Paul Chesnais, Antoine Pourchet, and Ryan Vogan

\newpage
\section{Introduction}
\label{sec:introduction}
  The Mississippi Emergency Management Administration (MSEMA) has hired our team to design hurricane evacuation routes for at-risk counties in the coastal regions of southern Mississippi. Given that this coastal area is a strong commercial center, the government authorities want us to minimize the number of unnecessary evacuations. Under this requirement, it is more advantageous to withhold evacuations for as long as safely possible. The reasons for this are two-fold. First, this ensures that local businesses can remain open for as long as possible. Second, this ensures that evacuation decisions are made when forecasts are most accurate. Therefore, our models seek to recommend an optimal evacuation plan as well as the latest possible time at which it is safe to enact this plan.
